An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-07-13 neurips-19/poly-embed.tex
remove old comment

  Applying (4) and (5) prove the theorem.
\end{proof}
\bo{Improving the above: may suffice to only consider unit vectors $v$. Claim is that it's associated with $\argmax_i (\nabla f_i)\cdot v$. Now show the set of $v$ associated with $f_i$ is compact, and that for each $v$, it's true that for all $u^*$ exposed by $v$ and all $u = u^* + \alpha v$ for some $\alpha > 0$, we have $f(u) \geq f(u^*) + c_v \cdot d(U,u)$.}

>>>>

  Applying (4) and (5) prove the theorem.
\end{proof}
